---
title: "Weight of Fish"
author: "Jared Lobitana"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
---

 setwd("C:/Users/16617/Documents/AVC/Math115/WUP_09")

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```

# Predicting Fish Weight
## get data
```{r}
fishData=read.csv("Fish.csv")
```


## Perch
```{r}
perch = filter(fishData, Species == "Perch")
```

### Best Models
```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=perch,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

The best two variables to predict weight are height and width.


### Best Two regressor model

The best two predictive regression model are height, width.

```{r}
perchModel= lm(Weight~Height+Width,data = perch)
summary(perchModel)
```

For the best model for adjusted r-square is 0.94

## Pike
```{r}
pike = filter(fishData, Species == "Pike")
```

### Best Models

```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=pike,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

The best model two variable to predict in weight are Length 1 and Length 3. 

### Best Two regressor model

The best two predictive regression model are Length 1 and Length 3.

```{r}
pikeModel= lm(Weight~Length1+Length3,data = pike)
summary(pikeModel)
```

For the best model for adjusted r-square is 0.9649

## Roach

```{r}
roach = filter(fishData, Species == "Roach")
```

### Best Models

```{r}
models = regsubsets(Weight ~ Length1+Length2+Length3+Height+Width, data=roach,
                    nvmax=5)

summary(models)

res.sum <- summary(models)
Adj.R2 = which.max(res.sum$adjr2)
print(paste("best adjusted r-squared", Adj.R2))

results = data.frame(
  Adj.R2 = which.max(res.sum$adjr2),
  CP = which.min(res.sum$cp),
  BIC = which.min(res.sum$bic)
)
print(results)

```

The best model two variable to predict in weight are Length 3 and Width. 

### Best Two regressor model

The best two predictive regression model are Length 1 and Width.

```{r}
roachModel= lm(Weight~Length3+Width,data = roach)
summary(roachModel)
```

The best model for adjusted r-square is 0.8482

## Final Summary Statements
To conclude, from lowest to highest adjusted r-square, among all of the models, the lowest will be the roach 0.8482 and the highest will be the pike which 0.9694 and second highest is the perch which is 0.94. Among these model the best is pike because we need the highest adjusted r-square for the best one.